Fail Faster

### 2025-03-24 paper/paper.tex
blah
devoid of thoughts

We isolate and quantify the performance benefits of faster randomness, showing
that a DSL's choice of \rand{} has a dramatic effect on its performance. Based
on the observation that the OCaml implementation of \bq{}'s \rand{} is slow in
an easy-to-fix way, we perform a controlled experiment, comparing fast and slow
versions of the same library to analyze the impact of faster \rand{} on
generator performance.

@@

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.60]{time.pdf}
  \caption{Time to generate values of varying sizes using each \camlname strategy. Lower is better. Both axes are logarithmic. BQ is \bq.}
  \label{fig:time}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.43]{bind.png}
  \caption{Left: Speedup from staging (compared to \bq) versus the number of \texttt{bind} calls.
  Right: Speedup from \csplitmix (compared to \camlname alone) versus the number of random samples.}
  \label{fig:binds}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.25]{scala.png}
 \caption{Time to generate values of varying sizes using each \scalaname strategy. Lower is better. Both axes are logarithmic. SC is ScalaCheck; Staged is \scalaname.}
 \label{fig:scala}
 \end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.46]{speedup.pdf}
  \caption{Geometric average of all speedups---relative to \bq---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board. CSM is \csplitmix.
  }
  \label{fig:etna}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.49]{swarm.png}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Gray dots represent tasks. Plots with extremely low variance have no swarm overlay. CSM is \csplitmix.}
  \label{fig:swarm}
\end{figure}

>>>>

We isolate and quantify the performance benefits of faster randomness, showing
that a DSL's choice of \rand{} has a dramatic effect on its performance. Based
on the observation that the OCaml implementation of \bq{}'s \rand{} is slow in
a way that is simple to fix, we perform a controlled experiment, comparing fast and slow
versions of the same library to analyze the impact of faster \rand{} on
generator performance.

@@

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.66]{time.pdf}
  \caption{Time to generate values of varying sizes using each \camlname strategy. Lower is better. Both axes are logarithmic. BQ is \bq.}
  \label{fig:time}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.46]{bind.pdf}
  \caption{Left: Speedup from staging (compared to \bq) versus the number of \texttt{bind} calls.
  Right: Speedup from \csplitmix (compared to \camlname alone) versus the number of random samples.}
  \label{fig:binds}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.66]{scala.pdf}
 \caption{Time to generate values of varying sizes using each \scalaname strategy. Lower is better. Both axes are logarithmic. SC is ScalaCheck; Staged is \scalaname.}
 \label{fig:scala}
 \end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.45]{speedup.pdf}
  \caption{Geometric average of all speedups---relative to \bq---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board. CSM is \csplitmix.
  }
  \label{fig:etna}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[scale=0.35]{swarm.pdf}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Gray dots represent tasks. Plots with extremely low variance have no swarm overlay. CSM is \csplitmix.}
  \label{fig:swarm}
\end{figure}
